Process_MCData

### 2024-03-18 Code/Process_MCData.Rmd
Edits to 'Intro' sections

Implement logistic and other growth curve fits to MultiCulti growth trajectories.

# Load Libraries and set project variables
Run only first time in session

```{r load libraries}
# libraries; Note check actual dependencies

>>>>

Implement logistic and other growth curve fits to MultiCulti growth trajectories. Individually tidied Muticultivator runs are imported from "Data/ImportedData/ImportedMCData" folder, processed and saved as .Rds in the "Data/ProcessedData/ProcessedMCData" folder. This script calculates deltaOD and filters data after x hours of decline growth from maximum in OD720 or deltaOD prior to implementing growth curve fits.

# Load Libraries and set project variables
Run only first time in session
```{r load libraries}
# libraries; Note check actual dependencies
